---
poster_height: "33.1in"
poster_width: "23.4in"
main_fontfamily: "Rasa"
font_family: "Rasa"
body_textsize: "33pt"
main_topsize: 0.13 #percent coverage of the poster
main_bottomsize: 0.08
primary_color: "#21618C"
secondary_colour: "#21618C"
accent_colour: "#21618C"
#ESSENTIALS
title: ''
column_numbers: 2
main_textsize: "120px"
author:
  - name: '**Filippo Gambarota**'
    affil: 1
    main: true
    #orcid: '0000-0002-6666-1747'
    twitter: fgambarota
    email: filippo.gambarota@unipd.it
  - name: Anna Vesely
    affil: 2
  - name: Livio Finos
    affil: 3
  - name: Gianmarco Altoè
    affil: 1
affiliation:
  - num: 1
    address: Department of Developmental and Social Psychology, University of Padova
  - num: 2
    address: Institute for Statistics, University of Bremen
  - num: 3
    address: Department of Statistics, University of Padova
main_findings:
  - "**joinmeta** - controlling the type-1 error in multiverse meta-analysis"
logoleft_name: "img/psicostat.png"
logoright_name: "img/unipd.png"
logocenter_name: "img/qrcode_final.svg"
knit: pagedown::chrome_print
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
    keep_md: true
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "80%")
options(knitr.table.format = "html") 
```

```{r packages}
library(tidyverse)
library(here)
library(cowplot)
```

```{r data}
multiverse <- readRDS(here("objects", "multiverse.rds"))
poster <- readRDS(here("poster", "poster.rds"))
multi_grid <- multiverse |> 
  select(rmorris, ragg, model) |> 
  distinct()

multi_sum <- readRDS(here("poster", "multi_sum.rds"))
res_sum <- readRDS(here("poster", "res_sum.rds"))


nmulti <- nrow(multi_grid)
```

```{r imgs}
imgs <- readRDS(here("poster", "img", "imgs.rds"))
```

# The Multiverse problem

```{r}
knitr::include_graphics("img/big-picture.svg")
```

**As example, we used the dataset by [Daros et al. (2021)](https://pubmed.ncbi.nlm.nih.gov/34545236/)** with a multivariate meta-analysis of RCTs designs with multiple measure for the same outcome. **We considered a total of `r nmulti`  plausible scenarios**.

# The Proposed Workflow

```{r, out.width="100%"}
knitr::include_graphics("img/workflow.svg")
```

We **simulated a plausible multiverse** sampling from a multivariate normal distribution with a vector of means (i.e., the meta-analysis results) and a variance-covariance matrix for the relationship between different scenarios.

</br>

# Multiverse Summary

```{r}
avg_multi <- sprintf("$%.3f$ ($SD = %.3f$)", mean(poster$res_sum$est), sd(poster$res_sum$est))
cors <- cor(poster$X)
cors <- cor(poster$X)[upper.tri(cor(poster$X))]
avg_cors <- sprintf("$%.3f$ ($SD = %.3f$)", mean(cors), sd(cors))
```

The multiverse is a associated with an **overall p-value $< 0.001$**, an **average effect  of `r avg_multi`** and an **average correlation of `r avg_cors`**.

```{r prep-plot}
multi_sum <- poster$res_sum |>
  select(est, p_flip)

multi_sum$p_flip <- log(multi_sum$p_flip)

multi_sum <- data.frame(b = c(multi_sum$est, rep(NA, length(cors) - nrow(multi_sum))),
                        praw = c(multi_sum$p_flip, rep(NA, length(cors) - nrow(multi_sum))),
                        r = cors)

multi_sum <- multi_sum |>
  pivot_longer(1:3)

multi_sum$name <- factor(multi_sum$name, labels = c("Effect Size", "P value (log)", "Correlation"))

# multiverse summary plot

multi_sum_plot <- multi_sum |>
  ggplot(aes(x = name, y = value, fill = name)) +
  geom_boxplot(show.legend = FALSE) +
  #gghalves::geom_half_violin(show.legend = FALSE, side = "l", nudge = 0.1) +
  #gghalves::geom_half_boxplot(show.legend = FALSE, side = "r", nudge = 0.1) +
  facet_wrap(~name, scales = "free") +
  theme_minimal(base_size = 25) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

# Impact of the correlation on the correction

r <- seq(0, 1, 0.01)

keff <- function(k, r){
  X <- r + diag(1 - r, k)
  L <- eigen(X)$values
  1 + (k - 1) * (1 - (var(L) / k))
}

cor_imp <- data.frame(
  r = r
)

ccor <- mean(cors)

cor_imp$keff <- sapply(r, function(x) keff(100, x))
cor_imp$pbonf <- 0.05 / cor_imp$keff

p_eff_test <- ggplot(cor_imp, aes(x = r, y = keff)) +
  geom_line() +
  #ggtitle(latex2exp::TeX("Impact of $\\rho$ on the number of effective tests")) +
  ylab(latex2exp::TeX("$t_{eff}$")) +
  xlab(latex2exp::TeX("Correlation ($\\rho$)")) +
  theme_minimal(base_size = 25)

p_alpha_reduction <- ggplot(cor_imp, aes(x = r, y = pbonf)) +
  geom_line() +
  #ggtitle(latex2exp::TeX("$\\alpha$ reduction as a function of $\\rho$")) +
  ylab(latex2exp::TeX("$\\alpha$")) +
  xlab(latex2exp::TeX("Correlation ($\\rho$)")) +
  theme_minimal(base_size = 25)

p_eff_test <- p_eff_test +
  geom_segment(x = ccor, xend = ccor, y = 0, yend = keff(100, ccor)) +
  geom_point(x = ccor, y = keff(100, ccor), size = 4, color = "firebrick3")

p_alpha_reduction <- p_alpha_reduction +
  geom_segment(x = ccor, xend = ccor, y = 0, yend = 0.05/keff(100, ccor)) +
  geom_point(x = ccor, y = 0.05/keff(100, ccor), size = 4, color = "firebrick3")

cor_impact <- plot_grid(p_eff_test, p_alpha_reduction)

title <- ggdraw() +
  draw_label(latex2exp::TeX("Impact of $\\rho$ on the number of effective tests"),
             size = 25,
             fontface='bold')
cor_impact <- plot_grid(title, p_eff_test,
                        ncol = 1, rel_heights = c(0.1, 1)) # rel_heights values
```

```{r, fig.height=3}
multi_sum_plot
```

```{r, fig.height=4}
cor_impact
```


# Multiverse post-hoc p-values

```{r}
# plotting raw and corrected p-values

pvals <- data.frame(praw = poster$res_sum$p_flip, padj = poster$res_sum$p.adj)

pvals |>
  mutate(sign = padj <= 0.05) |>
  ggplot(aes(x = praw, y = padj)) +
  geom_abline(linewidth = 1) +
  geom_vline(xintercept = 0.05, linetype = "dashed") +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_point(size = 3, aes(color = sign),
             show.legend = FALSE,
             alpha = 0.7) +
  theme_minimal(25) +
  theme(aspect.ratio = 1) +
  xlab("Raw P values") +
  ylab("maxT adjusted P values") +
  ylim(0, 0.25) +
  xlim(0, 0.25)
```

# Conclusions and Next Steps

- **Corrected p-values for valid post-hoc inference** on specific scenarios
- The method **control the Family-wise Error Rate (FWER)** across the multiverse
- **Fast meta-analysis via permutations** using the `flip` package
- Implementing multilevel and multivariate meta-analysis

```{css}
#main-img-left, #main-img-center, #main-img-right {
 width: 8%;
}

.main {
    width: 23.4in;
    height: calc(33.1in * 0.13);
    position: absolute;
    background-color: #21618C;
    color: white;
    font-family: Special Elite;
    background-image: linear-gradient(#21618C 50%,#21618C);
}

.main_bottom {
    width: 23.4in;
    height: calc(33.1in * 8.0e-2);
    margin-top: calc(33.1in * (1 - 8.0e-2));
    position: absolute;
    background-color: #21618C;
    background-image: linear-gradient(#21618C 50%,#21618C);
}

.section h1 {
    color: #1B4F72;
    text-align: center;
    padding-bottom: 5px;
    background: linear-gradient( to left, #ffffff 1%, #ffffff 20%, #21618C 33%, #21618C 50%, #21618C 66%, #ffffff 80%, #ffffff 99% ) left bottom #ffffff no-repeat;
    background-size: 100% 5px;
    margin-top: 0.5em;
    margin-bottom: 0.5em;
}

p strong {
    color: #C0392B;
}

ul strong {
    color: #C0392B;
}

#main-img-right {
    right: 0.5in;
    bottom: 0.45in;
    position: absolute;
}

#main-img-left {
    right: 0.5in;
    bottom: 0.4in;
    position: absolute;
}

.twitter, i {
    color: #8A8A8A;
    font-size: 35px;
    text-decoration: none;
}

a.email {
    text-decoration: none;
    color: #8A8A8A;
    font-size: 35px;
}

#author {
    color: #1B4F72;
    margin: 0;
    line-height: 85%;
    font-size: 1.17em;
}

h1 {
  font-size: 150%;
}
```

